### 2020-02-14 README.Rmd
Hijack the quanteda::corpus object
Streamline the validation process

A locked oolong test can be converted into a quanteda corpus for further analysis. The corpus contains two `docvars`, 'answer' and 'target_value'.

@@

```{r}
cor(all_afinn_score, docvars(gold_standard, "answer"))
```

```{r cor_afinn}
plot( docvars(gold_standard, "answer"), all_afinn_score)
```

>>>>

A locked oolong test can be converted into a quanteda-compatible corpus for further analysis. The corpus contains two `docvars`, 'answer' and 'target_value'.

@@

```{r}
docvars(gold_standard, "target_value") <- all_afinn_score
summarize_gold_standard(gold_standard)
```
